Dotted Suffix Trees\\A Structure for Approximate Text Indexing

### 2005-08-30 paper/construction.tex
fix references
s/mississipi/mississippi/

It is very simple to remove these nodes. As discussed above, suffix trees are normally implemented such that each node is actually just a pair of indices into the original string as shown in Figure~\ref{fig:mississipi-nodes}. To merge a child with its parent, we just need to replace both by a node whose starting index is the starting index of the original child minus the length of the parent edge. This process is illustrated in Figure~\ref{fig:merge}

>>>>

\begin{figure}
\includegraphics{merge}
\caption{Node Merging demonstration}%
\label{fig:merge}
\end{figure}

It is very simple to remove these nodes. As discussed above, suffix trees are normally implemented such that each node is actually just a pair of indices into the original string as shown in Figure~\ref{fig:mississippi-nodes}. To merge a child with its parent, we just need to replace both by a node whose starting index is the starting index of the original child minus the length of the parent edge. This process is illustrated in Figure~\ref{fig:merge}.

The construction of the tree using either Ukonnen or McCreight's algorithm assures one that this operation is always correct due to the way that the indices are created.
